### 2021-01-27 priority-gv.tex
Removed part of the higher-order typing example.

  \inferrule*{
    \tseq[\cs{o}]
    {\tmty{x'}{\tyrecv[\cs{o}]{\tyunit}{\tyendr}}}
    {\recv\;{x'}}
    {\typrod{\tyunit}{\tyendr}}
    \\
    \tseq[\cs{q}]
    {\tmty{y}{\tysend[\cs{o'}]{\tyunit}{\tyends}},\tmty{x'}{\tyendr}}
    {\letbind{y}{\send\;{\pair{\unit}{y}}}{\dots}}
    {\tyunit}
    \and
    \cs{o}<\cs{o'}
  }{%
    \tseq[\cs{q}]
    {%
      \tmty{y}{\tysend[\cs{o'}]{\tyunit}{\tyends}},
      \tmty{x'}{\tyrecv[\cs{o}]{\tyunit}{\tyendr}}
    }
    {\letpair{\unit}{x'}{\recv\;{x'}}{\letbind{y}{\send\;{\pair{\unit}{y}}}{\dots}}}
    {\tyunit}
  }
\end{mathpar}
Closures suspend communication, so \LabTirName{T-Lam} stores the priority bounds of the function body on the function type, and \LabTirName{T-App} restores them. For instance, $\tm{\lambda{x}.\send\;\pair{x}{y}}$ is assigned the type $\ty{\tylolli[\cs{o},\cs{o}]{A}{S}}$, \ie, a~function which, when applied, starts and finishes communicating at priority $\cs{o}$:
\begin{mathpar}
  \small
  \inferrule*{
    \inferrule*{
      \inferrule*{
      }{
        \tmty{\send}{\tylolli[\ptop,\cs{o}]{\typrod{A}{\tysend[\cs{o}]{A}{S}}}{S}}
      }
      \and
      \inferrule*{
        \inferrule*{
        }{
          \tseq[\pbot]{\tmty{x}{A}}{x}{A}
        }
        \and
        \inferrule*{
        }{
          \tseq[\pbot]
          {\tmty{x}{A},\tmty{y}{\tysend[\cs{o}]{A}{S}}}
          {y}{\tysend[\cs{o}]{A}{S}}
        }
      }{
        \tseq[\pbot]
        {\tmty{x}{A},\tmty{y}{\tysend[\cs{o}]{A}{S}}}
        {\pair{x}{y}}{\typrod{A}{\tysend[\cs{o}]{A}{S}}}
      }
    }{
      \tseq[\cs{o}]
      {\tmty{x}{A},\tmty{y}{\tysend[\cs{o}]{A}{S}}}
      {\send\;\pair{x}{y}}{S}
    }
  }{
    \tseq[\pbot]
    {\tmty{y}{\tysend[\cs{o}]{A}{S}}}
    {\lambda{x}.\send\;\pair{x}{y}}{\tylolli[\cs{o},\cs{o}]{A}{S}}
  }
\end{mathpar}
The approximation of the lower bound is not entirely accurate, \eg, $\tm{\lambda{x}.\send\;\pair{x}{y}}$ has lower bound $\ptop$, not $\cs{o}$, but as we only ever under-approximate, it is safe.

>>>>

  \inferrule*{
    \tseq[\cs{o}]
    {\tmty{x'}{\tyrecv[\cs{o}]{\tyunit}{\tyendr}}}
    {\recv\;{x'}}
    {\typrod{\tyunit}{\tyendr}}
    \\
    \tseq[\cs{q}]
    {\tmty{y}{\tysend[\cs{o'}]{\tyunit}{\tyends}},\tmty{x'}{\tyendr}}
    {\letbind{y}{\send\;{\pair{\unit}{y}}}{\dots}}
    {\tyunit}
    \and
    \cs{o}<\cs{o'}
  }{%
    \tseq[\cs{q}]
    {%
      \tmty{y}{\tysend[\cs{o'}]{\tyunit}{\tyends}},
      \tmty{x'}{\tyrecv[\cs{o}]{\tyunit}{\tyendr}}
    }
    {\letpair{\unit}{x'}{\recv\;{x'}}{\letbind{y}{\send\;{\pair{\unit}{y}}}{\dots}}}
    {\tyunit}
  }
\end{mathpar}
Closures suspend communication, so \LabTirName{T-Lam} stores the priority bounds of the function body on the function type, and \LabTirName{T-App} restores them. For instance, $\tm{\lambda{x}.\send\;\pair{x}{y}}$ is assigned the type $\ty{\tylolli[\cs{o},\cs{o}]{A}{S}}$, \ie, a~function which, when applied, starts and finishes communicating at priority $\cs{o}$.
\begin{mathpar}
  \small
  \inferrule*{
    \inferrule*{
      \inferrule*{
      }{
        \tmty{\send}{\tylolli[\ptop,\cs{o}]{\typrod{A}{\tysend[\cs{o}]{A}{S}}}{S}}
      }
      \and
      \inferrule*{%
        % \inferrule*{
        % }{
        %   \tseq[\pbot]{\tmty{x}{A}}{x}{A}
        % }
        % \and
        % \inferrule*{
        % }{
        %   \tseq[\pbot]
        %   {\tmty{x}{A},\tmty{y}{\tysend[\cs{o}]{A}{S}}}
        %   {y}{\tysend[\cs{o}]{A}{S}}
        % }
      }{
        \tseq[\pbot]
        {\tmty{x}{A},\tmty{y}{\tysend[\cs{o}]{A}{S}}}
        {\pair{x}{y}}{\typrod{A}{\tysend[\cs{o}]{A}{S}}}
      }
    }{
      \tseq[\cs{o}]
      {\tmty{x}{A},\tmty{y}{\tysend[\cs{o}]{A}{S}}}
      {\send\;\pair{x}{y}}{S}
    }
  }{
    \tseq[\pbot]
    {\tmty{y}{\tysend[\cs{o}]{A}{S}}}
    {\lambda{x}.\send\;\pair{x}{y}}{\tylolli[\cs{o},\cs{o}]{A}{S}}
  }
\end{mathpar}
